Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-06 paper/paper.tex
explaining questions/dimensions

%Should I Fuzz my Inputs or Improve my Tests? 
\title{Lessons Learned from Differential Testing JS Engines}

@@

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations. It is natural to expect that
such improvements will entail sensible changes in runtime
engines~\cite{kangax}; changes that could lead to errors. Finding bugs
on JS engines is an important problem. In this paper, we are
particularly interested in finding functional (non-crash) bugs.

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find
functional
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. DT
automates test generation in scenarios where multiple implementations
of a system exist. It leverages the diversity across system's
implementations to detect anomalous behavior. This paper reports the
results of a study we conducted to assess the impact of DT in finding
bugs on \js{} engines.

\Mar{this needs work$\rightarrow$} \Fix{but it has not been
  thoroughly explored to find functional bugs in JS engines. The
  closest work was done by Patra and Pradel~\cite{patra2016learning},
  where they evaluated their proposed language-agnostic fuzzer to find
  cross-browser HTML+JS discrepancies. This project aims at building
  and evaluating an infrastructure for differential testing of runtime
  engines, such as the JS engine or WebAssembly's. The sensible parts
  of the infrastructure are the checks of input validity (as to reduce
  waste/cost) and output correctness (as to reduce false positives).}

@@

%% methodology we used in our study.  The
%% dependent and independent variables will be discuss in
%% Section~\ref{sec:results}.

@@

\subsection{Seed JS files}~We considered in our study test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined test
suites from other repositories based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item The tests should be plug-and-play and/or easy
    integration.\Mar{not clear what you mean}
\end{itemize}

@@

@@

\Igor{
  In this section we discuss our findings to reach
  bugs in JS engines. Our experiments shows that fuzzing existents files
  still effective over the inputs without fuzzing.
}

\subsection{Dependent and Independent variables.}

The independent variable of our experiment is the fuzzing strategy as
implemented by various fuzzing tools. Our dependent variables are (i)
the ratio of bugs found with fuzzing versus no fuzzing and (ii) and
the ratio of bugs found with each fuzzing strategy. We consider a
search successful only if it lends in a bug confirmed by the
developers of the affected engine.  The rationale for considering the
ratio of bugs found with fuzzing versus no fuzzing is to observe how
often fuzzing really helps in this scenario. In the limit, all bugs
could be found without extra inputs, \ie{}, simply executing the seed
inputs on each engine and comparing their outcomes. Recall that we
mined test suites from a variety of sources. The rationale for
considering the fuzzing strategy is to understand to which extent each
strategy--as implemented by representative tools--helps in this
context.

\subsection{Fuzzing versus No Fuzzing}
\Fix{nao entendi muito sobre essa subsection... 
seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
\Igor{
  Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
  o sistema robusto nao significa que esta livre de bugs, ao contrario,
  estamos testando-o com simples entradas a partir de testes de regressao 
  de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
  para novos testcases. Partindo disso, realizar fuzzer em arquivos 
  existentes em projetos open-sources eh uma maneira de
  aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
  uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.

  Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 
  apenas 8 nao foram fuzzados \Fix{42.1\%}, isso se da 
  a importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
  \Fix{discuss}
}

\subsection{Fuzzing Strategy}
\Igor{
  Para realizar nossos experimentos, tivemos que decidir qual as 
  melhores abordagens para aumentar a efetividade dos fuzzers.
  Os fuzzers mutacionais se mostraram mais eficientes em relacao
  aos fuzzers geracionais, entao focamos neste ponto.
  Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
  default para realizar a mutacao em arquivos existentes.
  O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
  deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
  pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
  O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
  radamsa, gerando arquivos mais relevantes.
  Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
  é um arquivo de teste relevante, seguindo estes requisitos:
  \begin{itemize}
    \item it contains only unicode text
    \item it is parseable (i.e., it is structurally well-formed)
    \item it does not contain engine-specific functions  
    \item it does not empty
  \end{itemize}

@@

>>>>

%Should I Fuzz my Inputs or Improve my Tests? 
\title{Differential Testing Runtime Engines--Lessons Learned from the
  JavaScript Domain}

@@

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations. It is natural to expect that
such improvements will entail sensible changes in runtime
engines~\cite{kangax}; changes that could lead to errors. Finding bugs
on JS engines is an important problem.

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find
functional
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. DT
automates test generation in scenarios where multiple implementations
of a system exist. It leverages the diversity across system's
implementations to detect anomalous behavior.
%% WHAT WE DID
This paper reports the results of a study we conducted to assess the
ability of DT to find bugs on \js{} engines.  We analyzed
the impact of two orthogonal dimensions: test mining and fuzzing. The
first dimension, test mining, considers the effect that \js{} test
files mined from the repository of a given open-source engine have in
detecting functional bugs in other engines. The second dimension,
fuzzing, considers the impact of fuzzing the mined files in bug
detection.
%% WHAT WE FOUND
To sum, we found that \Fix{...}

%% LIST OF CONTRIBUTIONS
This paper makes the following contributions \Fix{...}

@@

@@

\subsection{Seed JS files\label{sec:seeds}}~We considered in our study test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined test
suites from other repositories based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item The tests should be plug-and-play and/or easy
    integration.\Mar{not clear what you mean}
\end{itemize}

@@

In this study, we analyzed the impact of two orthogonal dimensions in
bug finding: test mining and fuzzing. The first dimension focuses on
the impact of new inputs in bug finding whereas the second dimension
focuses on the impact of variations of existing inputs in bug finding.

\subsection{Test Mining}

In this experiment, we ran all tests (see Section~\ref{sec:seeds})
using our infrastructure in no-fuzzing mode. We inspected all warnings
reported by our tool and, for those we found suspicious, we filed a
bug report in the corresponding bug tracker.

\Igor{  
  Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 
  apenas 8 nao foram fuzzados \Fix{42.1\%}, isso se da 
  a importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
  \Fix{discuss}
}

%% \Fix{nao entendi muito sobre essa subsection... 
%% seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
%% \Igor{
%%   Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
%%   o sistema robusto nao significa que esta livre de bugs, ao contrario,
%%   estamos testando-o com simples entradas a partir de testes de regressao 
%%   de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
%%   para novos testcases. Partindo disso, realizar fuzzer em arquivos 
%%   existentes em projetos open-sources eh uma maneira de
%%   aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
%%   uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.

\subsection{Fuzzing}

The rationale for considering fuzzing as a dimension of study is to
assess the extent to which changing existing inputs helps in finding
new bugs. We measured this ability both in absolute terms and
relatively to the number of bugs found with the seed inputs in
no-fuzzing mode.

\Igor{
  Para realizar nossos experimentos, tivemos que decidir qual as 
  melhores abordagens para aumentar a efetividade dos fuzzers.
  Os fuzzers mutacionais se mostraram mais eficientes em relacao
  aos fuzzers geracionais, entao focamos neste ponto.
  Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
  default para realizar a mutacao em arquivos existentes.
  O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
  deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
  pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
  O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
  radamsa, gerando arquivos mais relevantes.
  Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
  é um arquivo de teste relevante, seguindo estes requisitos:
  \begin{itemize}
    \item it contains only unicode text
    \item it is parseable (i.e., it is structurally well-formed)
    \item it does not contain engine-specific functions  
    \item it does not empty
  \end{itemize}

@@

@@

\Fix{The
  closest work to ours was done by Patra and Pradel~\cite{patra2016learning},
  where they evaluated their proposed language-agnostic fuzzer to find
  cross-browser HTML+JS discrepancies. This project aims at building
  and evaluating an infrastructure for differential testing of runtime
  engines, such as the JS engine or WebAssembly's. The sensible parts
  of the infrastructure are the checks of input validity (as to reduce
  waste/cost) and output correctness (as to reduce false positives).}
